Robustly decorrelating errors with mixed quantum gates

### 2019-08-25 decorrelation/mixed_unitaries.tex
Text edits.

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{SQRTY_no_member.png}
  \caption{\kcy{Axis label is screwed up} Numerical results comparing a 0MQG to a 1MQG for a single tunable qubit, for $RY(\frac{\pi}{2})$. The results are qualitatively similar to those for $RX(\frac{\pi}{2})$. In this case the 0MQG outperforms both the 1MQG by two orders of magnitude, and the constituent controls by three orders of magnitude at the origin. However, varying over $\delta$ we see that the 1MQG outperforms the 0MQG by up to an order of magnitude when there is $.1\%$ drift in the qubit control amplitudes.}
  \label{fig:YMQG}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{2QRBC_no_member.png}
  \caption{\kcy{needs to be on previous page} Numerical results comparing a 0MQG to a 1MQG for a pair of tunable qubits, with a resonant exchange interaction. Shown with lower alpha values are example constituent controls. The 0MQG and 1MQG can be seen to outperform these controls by half of an order of magnitude at the origin. For all detuning values the 1MQG performs as well or better than the 0MQG. When there is $.2\%$ drift in the qubit frequency, the 1MQG outperforms members of the control families by almost an order of magnitude in diamond norm. Similarly, for $.2\%$ drift in the qubit control amplitude, we see that the 1MQG outperforms the the constituent controls by over half an order of magnitude.}
  \label{fig:2MQG}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{vectorspace2.pdf}
  \caption{A target unitary gate can be implemented a number of ways, each with a different effective Hamiltonian error. a) The error Hamiltonians shown with their derivative with respect to a control parameter. As this parameter drifts, a MQG may drift, leading to a first-order error. b) The derivatives also lie in a vector space. If the origin lies in their convex hull $\mathsf{Conv}(\{H_k \otimes H_{k,1} \oplus H_{k,2} \oplus \cdots\}_k)$ then it may be possible to construct a robust 1-MQG.}
  \label{fig:vectorspace}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\columnwidth]{SQRTY_no_member.png}
  \caption{\kcy{Axis label is screwed up} Numerical results comparing a 0MQG to a 1MQG for a single tunable qubit, for $RY(\frac{\pi}{2})$. The results are qualitatively similar to those for $RX(\frac{\pi}{2})$. In this case the 0MQG outperforms both the 1MQG by two orders of magnitude, and the constituent controls by three orders of magnitude at the origin. However, varying over $\delta$ we see that the 1MQG outperforms the 0MQG by up to an order of magnitude when there is $.1\%$ drift in the qubit control amplitudes.}
  \label{fig:YMQG}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{2q_robustness.png}
  \caption{\kcy{needs to be on previous page} Numerical results comparing a 0MQG to a 1MQG for a pair of tunable qubits, with a resonant exchange interaction. Shown with lower alpha values are example constituent controls. The 0MQG and 1MQG can be seen to outperform these controls by half of an order of magnitude at the origin. For all detuning values the 1MQG performs as well or better than the 0MQG. When there is $.2\%$ drift in the qubit frequency, the 1MQG outperforms members of the control families by almost an order of magnitude in diamond norm. Similarly, for $.2\%$ drift in the qubit control amplitude, we see that the 1MQG outperforms the the constituent controls by over half an order of magnitude.}
  \label{fig:2MQG}
\end{figure}
